proof-of-concept_mods

### 2023-10-20 proof-of-concept_mods.Rmd
setup to save csv with drop1 results as each model is fit

Visualize

@@

@@

ukb_df_age.filt <- ukb_df_age.filt %>%
  mutate(sexMale = as.numeric(case_when(sex == "Male" ~ 1,
                                        sex == "Female" ~ 0,
                                        TRUE ~ NA)))
model.test.refit <- gamlss(formula = lh_SA_superiortemporal ~ poly(age_days, 3) + sexMale,
                       sigma.formula = ~ poly(age_days, 3) + sexMale,
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)
drop1(model.test.refit, what = "sigma", scope = "sexMale")
```

>>>>

###Visualize

@@

##Troubleshooting

@@

ukb_df_age.filt <- ukb_df_age.filt %>%
  mutate(sexMale = as.numeric(case_when(sex == "Male" ~ 1,
                                        sex == "Female" ~ 0,
                                        TRUE ~ NA)))
model.test.refit <- gamlss(formula = lh_SA_superiortemporal ~ poly(age_days, 3) + sexMale,
                       sigma.formula = ~ poly(age_days, 3) + sexMale,
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)
drop1(model.test.refit, what = "sigma", scope = "sexMale")

model.test.refit2 <- gamlss(formula = lh_SA_superiortemporal ~ poly(age_days, 3) + sex,
                       sigma.formula = ~ poly(age_days, 3) + sex,
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)

drop.test.obj<-drop1(model.test.refit2, what = "nu")
df <- drop.test.obj %>%
  as.data.frame() %>%
  mutate(what=attributes(drop.test.obj)$heading[2]) %>%
  add_rownames(var = "term")

f <- drop1_all(model.test.refit2, name="TEST")
```
